Notes and approaches to OCR

### 2020-12-03 outputs/documents/paper.Rmd
PDF version

![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/outputs/documents/sections.png)
**Figure XX**

@@

![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
**Figure XX Section 1**

![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_2.png)
**Figure XX Section 2**

![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_3.png)
**Figure XX Section 3**

![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_4.png)
**Figure XX Section 4**

@@

NUmber of characters well recognized...(Accuracy)

>>>>

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
**Figure XX**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
**Figure XX Section 1**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_2.png)
**Figure XX Section 2**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_3.png)
**Figure XX Section 3**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_4.png)
**Figure XX Section 4**

@@

Number of characters well recognized...(Accuracy)
